# What Every File Does

```{r message=FALSE}
library(ggplot2)
library(dplyr)
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
# Packages needed internally, but not in book.
library(gapminder)
library(knitr)
library(kableExtra)
library(readr)
library(patchwork)
library(scales)
library(stringr)
```


```{r}
x = 5  # radius of a circle
```

For a circle with the radius `r x`,
its area is `r pi * x^2`.

```{r} 
source("can_you_read_me.R")
include_image("hello")
```

```{r, echo=FALSE}
gapminder_2007 <- gapminder %>% 
  filter(year == 2007) %>% 
  select(-year) %>% 
  rename(
    Country = country,
    Continent = continent,
    `Life Expectancy` = lifeExp,
    `Population` = pop,
    `GDP per Capita` = gdpPercap
  )
```

In February 2006, a Swedish physician and data advocate named Hans Rosling gave a TED talk titled ["The best stats you've ever seen"](https://www.ted.com/talks/hans_rosling_shows_the_best_stats_you_ve_ever_seen) where he presented global economic, health, and development data from the website [gapminder.org](http://www.gapminder.org/tools/#_locale_id=en;&chart-type=bubbles). For example, for data on `r nrow(gapminder_2007)` countries in 2007, let's consider only only a few countries in Table \@ref(tab:gapminder-2007) as a peak into the data.

